Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families

### 2020-03-14 manuscript/phylogenetic_signal_manuscript.tex
proofs changes
don't remember what changes

\author{Alyssa R. Cirtwill$^{\dagger1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$, Mikael Ohlsson$^{4}$,\\ 
Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$, Joshua A. Thia$^{1}$, Daniel B. Stouffer$^{1}$}
\date{
\begin{multicols}{2}
\small
$\dagger$ Corresponding author: alyssa.cirtwill@gmail.com; +46 8 16 20 00\\
\medskip$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\bigskip\bigskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\ \medskip
\end{multicols}}

@@

% \clearpage
\vspace{-0.5in}
\section*{ORCID IDs}
\noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
\noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
\noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
\noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\

\vspace{-0.25in}
\section*{Word Counts}
\begin{multicols}{2}

Main text: 6409 % Limit 6,500 % 
\vspace{-5pt}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item Introduction: 1163
  \item Materials and Methods: 2469
  \item Results: 949
  \item Discussion: 1745
  \item Acknowledgements: 83
\end{itemize}

\noindent Figures: 3\\
\noindent Tables: 2\\
\noindent Notes: 1 file, 6 sections.
\end{multicols}

\vspace{-0.25in}
\begin{multicols}{2}
\section*{Social media}
@acirtwill; @stoufferlab\\

\section*{Header}

@@

>>>>

\author{Alyssa R. Cirtwill$^{\dagger1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$, Mikael Ohlsson$^{4}$,\\ 
Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$, Joshua A. Thia$^{1}$, \& Daniel B. Stouffer$^{1}$}
\date{
\begin{multicols}{2}
\small
$\dagger$ Corresponding author: alyssa.cirtwill@gmail.com; +46 8 16 20 00\\
\medskip$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\bigskip\bigskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\ \medskip
\end{multicols}}

@@

\noindent This is the accepted version of the following article: \\
\smallskip
Cirtwill, A. R., Dalla Riva, G. V., Baker, N. J., Ohlsson, M.,
Norstr\"{o}m$^{4}$, I., Wohlfarth, I. M., Thia, J. A., Stouffer, D. B. (2020) \emph{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}. \textbf{New Phytologist}: in press, which has been published in final form at \emph{link to paper}.\\
\smallskip
This article may be used for
non-commercial purposes in accordance with the Wiley Self-Archiving Policy [http://www.wileyauthors.com/self-archiving].

% % \clearpage
% \vspace{-0.25in}
% \small{
% \noindent\textbf{ORCID IDs}\\
% \noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
% \noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
% \noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
% \noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\

% \medskip
% \noindent\textbf{Social media}: 
% @acirtwill; @stoufferlab\\
% \medskip
% \noindent\textbf{Header}: 
% Phylogenetic distance \& niche overlap
% }

% \noindent\small\textbf{Word Counts}
% \begin{multicols}{2}
% \small{
% Main text: 6409 % Limit 6,500 % 
% \vspace{-5pt}
% \begin{itemize}
%   \setlength\itemsep{-0.1em}
%   \item Introduction: 1163
%   \item Materials and Methods: 2469
%   \item Results: 949
%   \item Discussion: 1745
%   \item Acknowledgements: 83
% \end{itemize}
% \bigskip
% \bigskip
% \bigskip

% \noindent Figures: 3\\
% \noindent Tables: 2\\
% \noindent Notes: 1 file, 6 sections.}
% \end{multicols}

@@

\newpage
